Strict Pure Functional Programming and Automatic Parallelization and Transparent Fault Tolerance\\ (New-project-in-progress Paper)

### 2016-03-28 pubs/tfp16/paper.tex

{\color{red}\dots}

>>>>

STG supports pattern matching but only in a simple form and only in
\texttt{case} expressions.  mini-Haskell extends this to something approaching
what is found in Haskell.  Functions, including lambda expressions, may match on
all their arguments (with multiple non-anonymous definitions allowed to exhaust
the pattern combinations).  Patterns in all contexts (functions and case
expressions) may be nested arbitrarily deep.  These two features greatly
simplify the programmer's job.
